---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SJDB

<!-- badges: start -->

<!-- badges: end -->

SJDB is a R package of run RNA-seq DEGs analysis for Schistosoma japonicum

## Installation

You can install the development version of SJDB like so:

``` r
install.packages('SJDB/',repos = NULL)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SJDB)
# If you want to do GO and KEGG pathway analysis for Schistosoma joponicum,you must install org.Sjaponicum.eg.db firstly,like this:

# install.packages(paste0(system.file("extdata",package = "SJDB"),"/org.Sjaponicum.eg.db"),repos = NULL)

library(org.Sjaponicum.eg.db)
## basic example code

```

```{r load-packages, include=FALSE}

library(writexl)
library(DESeq2)
library(clusterProfiler)
library(ggplot2)
library(FactoMineR)
library(factoextra)
library(patchwork)
library(ggpubr)
library(org.Sjaponicum.eg.db)
library(EnhancedVolcano)
```

### Step1.run different expression analysis and get a dds object

```{r echo=FALSE}

dds <- run_DESeq2(count_data = '~/Projects/RNASeq_YC_20220810/2.Results/SnakePipe_outputs/featureCounts/counts.tsv',group_a_name = 'GFP',group_a_samples = c("GFP.F1", "GFP.F2", "GFP.F3", "GFP.F4"),group_b_name = 'One2',group_b_samples = c("One2.F1", "One2.F2", "One2.F3", "One2.F4"))

# ,save_Plot = T,file_Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/',p_cutoff = 0.05,FC_cutoff = 1

```

### Step2.PCA and Sample Correlation Analysis(pearson)

If you want to save plots,just set `save_Plot = T, file_Dir = 'your_path/'`

```{r echo=FALSE}
plot_PCA(dds,save_Plot = T,file_Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/')

```

```{r echo=FALSE}

Plot_corr_heatmap(dds,savePlot = T,fileDir = '~/Projects/RNASeq_YC_20220810/2.Results/test/',type = 'pearson')


```

### Step3.Get the DEGs(different expression genes) you want

```{r echo=FALSE}

diffres <- get_mRNA_diff(dds,x= 'GFP',y = 'One2',p_cutoff = 0.05,FC_cutoff = 1)

```

### Step4.Heatmap and volcano plot

```{r echo=FALSE,warning=FALSE}
Plot_volcano(Diff_res = diffres,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/',save_Plot = T )

```

optional

```{r echo=FALSE,warning=FALSE,fig.height=8,fig.width=6}
Plot_enhancedVolcano(Diff_res = diffres,n = 5,save_Plot = T,p_cutoff = 0.05,FC_cutoff = 1,Dir ='~/Projects/RNASeq_YC_20220810/2.Results/test/' )

```

```{r echo=FALSE,warning=FALSE,fig.width=3.5,fig.height=6}
Plot_heatmap(Diff_res = diffres,dds = dds,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/',
             save_Plot = T,show_rownames = F)
```

```{r echo=FALSE,warning=FALSE}
Barplot_ID(dds = dds,ID = 'Sjc_0003510')
```

### Step5.GO / KEGG pathway enrichment analysis ps: optional,not required

```{r echo=FALSE}
GOres <- getGO(diffres$down_gene$SYMBOL)
clusterProfiler::cnetplot(GOres$GOList$MF) # BP,CC,MF
```

```{r echo=FALSE}
KEGGres <- getKEGG(diffres$down_gene$SYMBOL)
clusterProfiler::dotplot(KEGGres)
```

```{r echo=FALSE}
Plot_DE_GOTerms(Diff_res = diffres,DIR = '~/Projects/RNASeq_YC_20220810/2.Results/test/',p_cutoff = 0.05)
```

### Step6.Write results to excel files

```{r echo=FALSE}
ExptoXlSX(dds = dds,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/')
DEtoXlSX(Diff_res = diffres,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/')
GOtoXlSX(Diff_res = diffres,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/')
# GSEA analysis need long time,don't run in the example 
# GSEAtoXlSX(Diff_res = diffres,Dir = '~/Projects/RNASeq_YC_20220810/2.Results/test/',pvalueCutoff = 0.5)

list.files("~/Projects/RNASeq_YC_20220810/2.Results/test/",pattern = '*xlsx')
```
